Expected Dependency Pair Match:\\ Predicting {HTER} improvements with expected syntactic structure

### 2009-05-10 mtjournal.tex
corpus stats for GALE 2.5 corpus

\section{Per-document correlations with HTER}
\label{sec:hter1}
  Corpus
    Gale translation corpus 2.5; 3 sites, 2 source languages, 4 genres each

@@

  (Go into details of per-genre differences here? or leave out, for
  space reasons? -- leave out, I'd say)

>>>>

\section{Per-document correlations with HTER}
\label{sec:hter1}
TO DO: INTRODUCE THIS SECTION

The GALE 2.5 translation corpus is made up of system translations into
English from three sites.
% MO added:
The three sites all use system combination to integrate results from
multiple systems, some of which are phrase-based and some which may
use syntax on either the source or target side. No system provided
system-generated parses.
%
The corpus being translated comes from
Arabic and Chinese in four genres: \texttt{bc} (broadcast
conversation), \texttt{bn} (broadcast news), \texttt{nw} (newswire),
and \texttt{wb} (web text), with corpus sizes shown in
table~\ref{tab:galestats}.
\begin{table}
%  \centering
  \begin{tabular}{r|rr|rr|rr}
     & \multicolumn{2}{c|}{Arabic} & \multicolumn{2}{c|}{Chinese}
     & \multicolumn{2}{c}{Total}\\
     & doc & sent & doc & sent & doc   & sent\\
     \hline
     \texttt{bc}    & 59  & 750 & 56 & 1061 & 115 & 1811\\
     \texttt{bn}    & 63  & 666 & 63 & 620  & 126 & 1286\\
     \texttt{nw}    & 68  & 494 & 70 & 440  & 138 & 934 \\
     \texttt{wb}    & 69  & 683 & 68 & 588  & 137 & 1271\\
     \hline
     Total & 259 & 2593& 257& 2709 & 516 & 5302\\
  \end{tabular}
  \caption{Corpus statistics for the GALE 2.5 translation
    corpus.}
  \label{tab:galestats}
\end{table}
The corpus includes one English reference translation $r_i$
\cite{gale08phase2_5references} for each sentence $i$ and a system
translation $t_{i,z}$ for each of the three systems
$z$. Additionally, each of the system translations of each segment $i$
has a corresponding human-targeted reference aligned at the sentence
level, so we have available the HTER score of each segment
$s_{\textsc{hter}}(t_{i,z})$ at both the sentence and document level.

@@

  include genre tables here as well -- cut out again if no story.
